Brownian Dynein Model

### 2015-10-25 latex/derivation.tex
Add small redo of Xt derivative.

\subsection{$X_t$}
\begin{align*}
  X_t &= X_{nm} + L_t\cos(\theta_1 \pm \theta_2)\\
  &= X_{nm} + L_t\cos\left(\cos^{-1}\left(\frac{X_{fm}-X_{nm}}{L}\right) \pm \cos^{-1}\left(\frac{L}{2L_t}\right) \right)
  \hspace*{1in} \cos\Big(cos^{-1}(a)\pm cos^{-1}(b)\Big) = ab \mp \sqrt{1-a^2}\sqrt{1-b^2}\\
  &= X_{nm} + L_t\left(\frac{X_{fm}-X_{nm}}{2L_t} \mp \sqrt{1 - \frac{\left(X_{fm}-X_{nm}\right)^2}{L^2}}\sqrt{1 - \frac{L^2}{4L_t^2}}\right)\\
  &= \frac{X_{fm}+X_{nm}}{2} \mp \frac{1}{2}\sqrt{1 - \frac{\left(X_{fm}-X_{nm}\right)^2}{L^2}}\sqrt{4L_t - L^2}\\
  &= \frac{X_{fm}+X_{nm}}{2} \mp \frac{1}{2L}\sqrt{L^2 - \left(X_{fm}-X_{nm}\right)^2}\sqrt{4L_t - L^2}\\
  &= \frac{X_{fm}+X_{nm}}{2} \mp \frac{1}{2}\sqrt{(Y_{fm}-Y_{nm})^2}\sqrt{\frac{4L_t}{L^2} - 1}\\
  &= \frac{X_{fm}+X_{nm}}{2} \mp \frac{Y_{fm}-Y_{nm}}{2L}\sqrt{\frac{4L_t^2}{\left(X_{fm}-X_{nm}\right)^2 + \left(Y_{fm}-Y_{nm}\right)^2} -1}\\
  &= \frac{X_{fm}+X_{nm}}{2} \mp \frac{Y_{fm}-Y_{nm}}{2}\sqrt{\frac{4L_t^2}{X_{fm}^2 + X_{nm}^2 + Y_{fm}^2 + Y_{nm}^2 -2X_{fm}X_{nm} -2Y_{fm}Y_{nm}} -1}\\
  &= \frac{B + L_s\cos(\theta_{fb}) + L_s\cos(\theta_{nb})}{2} \mp \frac{L_s\sin(\theta_{fb})-L_s\sin(\theta_{nb})}{2} * \\
  &\sqrt{\frac{4L_t^2}{B^2 + L_s^2\cos^2(\theta_{fb}) + 2BL_s\cos(\theta_{fb}) + L_s^2\cos^2(\theta_{nb}) + L_s^2\sin^2(\theta_{fb}) + L_s^2\sin^2(\theta_{nb}) -2(B + L_s\cos(\theta_{fb}))(L_s\cos(\theta_{nb})) -2L_s^2\sin(\theta_{fb})\sin(\theta_{nb})} -1}\\\\
  &= \frac{B + L_s\cos(\theta_{fb}) + L_s\cos(\theta_{nb})}{2} \mp \frac{L_s\sin(\theta_{fb})-L_s\sin(\theta_{nb})}{2} * \\
  &\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb})\cos(\theta_{nb}) - 2L_s^2\sin(\theta_{fb})\sin(\theta_{nb})} -1}\\\\
  &= \frac{B + L_s\cos(\theta_{fb}) + L_s\cos(\theta_{nb})}{2} \mp \frac{L_s\sin(\theta_{fb})-L_s\sin(\theta_{nb})}{2}\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} -1}\\
\end{align*}

>>>>

\subsection{$X_t$}
\begin{align*}
  X_t &= X_{nm} + L_t\cos(\theta_1 \pm \theta_2)\\
  &= X_{nm} + L_t\cos\left(\cos^{-1}\left(\frac{X_{fm}-X_{nm}}{L}\right) \pm \cos^{-1}\left(\frac{L}{2L_t}\right) \right)
  \hspace*{1in} \cos\Big(cos^{-1}(a)\pm cos^{-1}(b)\Big) = ab \mp \sqrt{1-a^2}\sqrt{1-b^2}\\
  &= X_{nm} + L_t\left(\frac{X_{fm}-X_{nm}}{2L_t} \mp \sqrt{1 - \frac{\left(X_{fm}-X_{nm}\right)^2}{L^2}}\sqrt{1 - \frac{L^2}{4L_t^2}}\right)\\
  &= \frac{X_{fm}+X_{nm}}{2} \mp \frac{1}{2}\sqrt{1 - \frac{\left(X_{fm}-X_{nm}\right)^2}{L^2}}\sqrt{4L_t - L^2}\\
  &= \frac{X_{fm}+X_{nm}}{2} \mp \frac{1}{2L}\sqrt{L^2 - \left(X_{fm}-X_{nm}\right)^2}\sqrt{4L_t - L^2}\\
  &= \frac{X_{fm}+X_{nm}}{2} \mp \frac{1}{2}\sqrt{(Y_{fm}-Y_{nm})^2}\sqrt{\frac{4L_t}{L^2} - 1}\\
  &= \frac{X_{fm}+X_{nm}}{2} \mp \frac{Y_{fm}-Y_{nm}}{2L}\sqrt{\frac{4L_t^2}{\left(X_{fm}-X_{nm}\right)^2 + \left(Y_{fm}-Y_{nm}\right)^2} -1}\\
  &= \frac{X_{fm}+X_{nm}}{2} \mp \frac{Y_{fm}-Y_{nm}}{2}\sqrt{\frac{4L_t^2}{X_{fm}^2 + X_{nm}^2 + Y_{fm}^2 + Y_{nm}^2 -2X_{fm}X_{nm} -2Y_{fm}Y_{nm}} -1}\\
  &= \frac{B + L_s\cos(\theta_{fb}) + L_s\cos(\theta_{nb})}{2} \mp \frac{L_s\sin(\theta_{fb})-L_s\sin(\theta_{nb})}{2} * \\
  &\sqrt{\frac{4L_t^2}{B^2 + L_s^2\cos^2(\theta_{fb}) + 2BL_s\cos(\theta_{fb}) + L_s^2\cos^2(\theta_{nb}) + L_s^2\sin^2(\theta_{fb}) + L_s^2\sin^2(\theta_{nb}) -2(B + L_s\cos(\theta_{fb}))(L_s\cos(\theta_{nb})) -2L_s^2\sin(\theta_{fb})\sin(\theta_{nb})} -1}\\\\
  &= \frac{B + L_s\cos(\theta_{fb}) + L_s\cos(\theta_{nb})}{2} \mp \frac{L_s\sin(\theta_{fb})-L_s\sin(\theta_{nb})}{2} * \\
  &\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb})\cos(\theta_{nb}) - 2L_s^2\sin(\theta_{fb})\sin(\theta_{nb})} -1}\\\\
  &= \frac{B + L_s\cos(\theta_{fb}) + L_s\cos(\theta_{nb})}{2} \mp \frac{L_s\sin(\theta_{fb})-L_s\sin(\theta_{nb})}{2}\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} -1}\\
  \dot{X}_t &= \frac{-L_s\sin(\theta_{fb})\dot{\theta}_{fb} - L_s\sin(\theta_{nb})\dot{\theta}_{nb}}{2}\\
  &\mp \frac{d}{dt} \left(\frac{L_s\sin(\theta_{fb})-L_s\sin(\theta_{nb})}{2}\right)\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} -1}\\
  &\mp \frac{L_s\sin(\theta_{fb})-L_s\sin(\theta_{nb})}{2}\frac{d}{dt} \left(\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} -1}\right)\\
   \dot{X}_t &= \frac{-L_s\sin(\theta_{fb})\dot{\theta}_{fb} - L_s\sin(\theta_{nb})\dot{\theta}_{nb}}{2}\\
  &\mp \left(\frac{L_s\cos(\theta_{fb})\dot{\theta}_{fb} - L_s\cos(\theta_{nb})\dot{\theta}_{nb}}{2}\right)\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} -1}\\
   &\mp \frac{L_s\sin(\theta_{fb})-L_s\sin(\theta_{nb})}{2}\left(\frac{1}{2\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} -1}}\right) *\\
   &\left(\frac{-4L_t^2}{\left(2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})\right)^2}\right) *\\
   &\left(-2BL_s\sin(\theta_{fb})\dot{\theta}_{fb} + 2BL_s\sin(\theta_{nb})\dot{\theta}_{nb} + 2L_s^2\sin(\theta_{fb} - \theta_{nb})(\dot{\theta}_{fb}-\dot{\theta}_{nb})\right)\\
   \dot{X}_t &= \frac{-L_s\sin(\theta_{fb})\dot{\theta}_{fb} - L_s\sin(\theta_{nb})\dot{\theta}_{nb}}{2}\\
  &\mp \left(\frac{L_s\cos(\theta_{fb})\dot{\theta}_{fb} - L_s\cos(\theta_{nb})\dot{\theta}_{nb}}{2}\right)\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} -1}\\
   &\mp \frac{L_s\sin(\theta_{fb})-L_s\sin(\theta_{nb})}{2}\left(\frac{\left(\frac{-4L_t^2\left(-2BL_s\sin(\theta_{fb})\dot{\theta}_{fb} + 2BL_s\sin(\theta_{nb})\dot{\theta}_{nb} + 2L_s^2\sin(\theta_{fb} - \theta_{nb})(\dot{\theta}_{fb}-\dot{\theta}_{nb})\right)}{\left(2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})\right)^2}\right)}{2\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} -1}}\right)\\
\end{align*}
